---
title: "BOM_data_blog"
author: "P. Melloy"
date: "11 July 2019"
output: html_document
---

This is a file which will hopefully serve as inspiration for a blog.

The idea is to show the users through using R in QGIS by doing the following tasks:  
   -  Finding the R integration  
   -  Loading a library bomrang  
   -  Using get historical to download weather data  
   -  Save the file as a csv  
   -  import the station location data into QGIS using lat and longs
   -  
   
```{r}
#install.packages("bomrang")
#remove.packages("bomrang")
devtools::install_github("melloy/bomrang")
library(bomrang)
library(dplyr)

```

## Obtain station information   
First we are going to find the BOM stations near the point of interest.  

```{r obtain data}

# subset BOM stations by distance of 200km from latlon.
stations <- sweep_for_stations(latlon = c(-26.56, 151.93))
stations <- subset(stations, distance <= 150)

station_data <- lapply(stations$site, 
                       get_historical,
                       type = "max")

```


Now we need to clean and and write our data to csv. Currently it is in a list form, where each element of the list contains a data frame of maximum temperature data from each weather station.  

We need one dataset with all the weather data and the latitude and longitudes, but we have two datasets one with the weather data and one with the weather station information. The following steps gets us the data we need to save it to csv.
   1. Collapes the `list` into a `data.frame` with `bind_rows`  
   2. Rename the station identifier code in both `data.frames` to the same name so `merge` will work  
   3. Ensure the `station_number` is in the same format (numeric) for matching and merging.  
   4. Merge into `station_data` only the columns (3) station name, (6) latitude, (7) longitude.
   5. Create column `date` from other columns in SI format
   6. Save the data into our working directory
   7. Create an additional dataset of a single day
   
```{r}
station_data <- dplyr::bind_rows(station_data)


colnames(stations)[1] <- colnames(station_data)[2] # 
stations$station_number <- as.numeric(stations$station_number)
station_data$station_number <- as.numeric(station_data$station_number)

station_data <- merge(station_data, stations[,c(1,3,6,7)], all.x = TRUE)

station_data$date <- as.character(paste(station_data$year,
                                        station_data$month,
                                        station_data$day,
                                        sep = "-"))

getwd() # This is where we will save the temperature data
write.csv(station_data, "./Max_temp_data.csv")
write.csv(subset(station_data, date == "2019-1-5"), "./190105_Max_temp.csv")
```

